Outline

### 2020-12-30 text/main.Rmd
minor edit

# Global drivers and vulnerabilities of coral reef fish functions

Nina M. D. Schiettekatte^1,2^, Simon J. Brandl^3^, Jordan M. Casey^3^, Nicholas A. J. Graham^4^, Diego R. Barneche^5,6^, Deron E. Burkepile^7,8^, Jacob E. Allgeier^9^, Jesús E. Arias-Gonzaléz^10^, Graham J. Edgar^11^, Carlos E. L. Ferreira^12^, Sergio R. Floeter^13^, Alan M. Friedlander^14^, Alison L. Green^15^, Michel Kulbicki^2,16^, Yves Letourneur^2,17^, Osmar J. Luiz^18^, Alexandre Mercière^1,2^, Fabien Morat^1,2^, Katrina S. Munsterman^9^, Enrico L. Rezende^19^, Fabian A. Rodríguez‐Zaragoza^20^, Rick D. Stuart-Smith^11^, Laurent Vigliola^2,16^, Sébastien Villéger^21^, Valeriano Parravicini^1,2^

^1^PSL Université Paris: EPHE-UPVD-CNRS, USR 3278 CRIOBE, Université de Perpignan, Perpignan, France;
^2^Laboratoire d'Excellence “CORAIL”, Perpignan, France;
^3^The University of Texas at Austin, Marine Science Institute, Port Aransas, TX 78373, USA;
^4^Lancaster Environment Centre, Lancaster University, Lancaster, LA1 4YQ, UK;
^5^Australian Institute of Marine Science, Crawley, WA, Australia;
^6^Oceans Institute, The University of Western Australia, Crawley, WA, Australia;
^7^Department of Ecology, Evolution, and Marine Biology, University of California, Santa Barbara, CA, USA;
^8^Marine Science Institute, University of California, Santa Barbara, CA, USA;
^9^Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, MI, USA;
^10^Laboratorio Ecología de Ecosistemas de Arrecifes Coralinos, Departamento Recursos del Mar, CINVESTAV Unidad Mérida, AP73 Cordemex, CP97310, Mérida, Yucatán, Mexico;
^11^Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, TAS, Australia;
^12^Departamento de Biologia Marinha, Universidade Federal Fluminense (UFF), Niterói,  the state of Rio de Janeiro (RJ), Brazil;
^13^Marine Macroecology and Biogeography Lab, Depto. de Ecologia e Zoologia, CCB, Universidade Federal de Santa Catarina, Florianopolis, Santa Catarina, Brazil;
^14^Department of Biology, University of Hawaii, Honolulu, HI, USA;
^15^Red Sea Research Center, King Abdullah University of Science and Technology, Thuwal 23955-6900, Saudi Arabia;
^16^Institut de Recherche pour le Développement, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;
^17^Université de la Nouvelle-Calédonie, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;
^18^Research Institute for the Environment and Livelihoods, Charles Darwin University, Darwin, Australia;
^19^Departamento de Ecología, Center of Applied Ecology and Sustainability (CAPES), Facultad de Ciencias Biológicas, Pontificia Universidad Católica de Chile, Santiago 6513677, Chile;
^20^Laboratorio de Ecosistemas Marinos y Acuicultura (LEMA), Departamento de 12 Ecología, CUCBA, Universidad de Guadalajara. México. Carr. Guadalajara-Nogales 13 km. 15.5, Las Agujas Nextipac, Zapopan, C.P. 45110, Jalisco, 14, Mexico;
^21^MARBEC, Université de Montpellier, CNRS, IFREMER, IRD, Montpellier, France

## Abstract

Preserving the integrity of coral reefs – their functioning – is a critical challenge of the 21st century. 
However, a quantitative assessment of multiple functions is needed to guide conservation efforts. 
Through the integration of empirically-parametrized bioenergetic models and global community surveys, we quantify five key functions mediated by fishes. 
We show that functions exhibit critical trade-offs driven by diverging community structures. 
Further, functions are locally dominated by few species, but worldwide, the identity of dominant species varies a lot - 70% of the 1110 species in our dataset are locally dominant. 
Our quantitative assessment reveals a challenge in global coral reef conservation: no reef fish community can simultaneously sustain high values across all functions and there are no global keystone species to target.

## Main Text

The flow of elements through biological communities fuels all life on Earth [@Welti2017]. Preserving these fluxes, often termed ecosystem functions, is critical for the integrity of ecosystems [@Welti2017].
For millennia, resources have been managed with an economic mindset to maximize desirable functions such as the production of plant or animal biomass [@Weisser2017].
Sustaining multiple functions likely requires both high species richness and a variety of species assemblages across a landscape [@Zavaleta2010].
However, in agro-ecological settings, efforts to maximize one function negatively impact another (e.g. timber production vs. erosion control), shedding light on the existence of trade-offs between functions [@Tallis2008; @Zavaleta2010].
An understanding of such trade-offs is required to make informed management decisions [@Rodriguez2006], but simultaneously quantifying multiple ecosystem functions is challenging.
Therefore, trade-offs between functions, their drivers, and functional vulnerability are poorly understood in many ecosystems [@Brandl2019front].

>>>>

# **Title:** Global drivers and vulnerabilities of coral reef fish functions

**Authors:** Nina M. D. Schiettekatte^1,2,*^, Simon J. Brandl^3^, Jordan M. Casey^3^, Nicholas A. J. Graham^4^, Diego R. Barneche^5,6^, Deron E. Burkepile^7,8^, Jacob E. Allgeier^9^, Jesús E. Arias-Gonzaléz^10^, Graham J. Edgar^11^, Carlos E. L. Ferreira^12^, Sergio R. Floeter^13^, Alan M. Friedlander^14^, Alison L. Green^15^, Michel Kulbicki^2,16^, Yves Letourneur^2,17^, Osmar J. Luiz^18^, Alexandre Mercière^1,2^, Fabien Morat^1,2^, Katrina S. Munsterman^9^, Enrico L. Rezende^19^, Fabian A. Rodríguez‐Zaragoza^20^, Rick D. Stuart-Smith^11^, Laurent Vigliola^2,16^, Sébastien Villéger^21^, Valeriano Parravicini^1,2^

^1^PSL Université Paris: EPHE-UPVD-CNRS, USR 3278 CRIOBE, Université de Perpignan, Perpignan, France;    
^2^Laboratoire d'Excellence “CORAIL”, Perpignan, France;     
^3^The University of Texas at Austin, Marine Science Institute, Port Aransas, TX 78373, USA;      
^4^Lancaster Environment Centre, Lancaster University, Lancaster, LA1 4YQ, UK;      
^5^Australian Institute of Marine Science, Crawley, WA, Australia;      
^6^Oceans Institute, The University of Western Australia, Crawley, WA, Australia;      
^7^Department of Ecology, Evolution, and Marine Biology, University of California, Santa Barbara, CA, USA;      
^8^Marine Science Institute, University of California, Santa Barbara, CA, USA;      
^9^Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, MI, USA;      
^10^Laboratorio Ecología de Ecosistemas de Arrecifes Coralinos, Departamento Recursos del Mar, CINVESTAV Unidad Mérida, AP73 Cordemex, CP97310, Mérida, Yucatán, Mexico;      
^11^Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, TAS, Australia;      
^12^Departamento de Biologia Marinha, Universidade Federal Fluminense (UFF), Niterói,  the state of Rio de Janeiro (RJ), Brazil;     
^13^Marine Macroecology and Biogeography Lab, Depto. de Ecologia e Zoologia, CCB, Universidade Federal de Santa Catarina, Florianopolis, Santa Catarina, Brazil;      
^14^Department of Biology, University of Hawaii, Honolulu, HI, USA;      
^15^Red Sea Research Center, King Abdullah University of Science and Technology, Thuwal 23955-6900, Saudi Arabia;
^16^Institut de Recherche pour le Développement, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;     
^17^Université de la Nouvelle-Calédonie, UMR UR-IRD-CNRS-IFREMER-UNC ENTROPIE, Nouméa, New Caledonia, France;     
^18^Research Institute for the Environment and Livelihoods, Charles Darwin University, Darwin, Australia;     
^19^Departamento de Ecología, Center of Applied Ecology and Sustainability (CAPES), Facultad de Ciencias Biológicas, Pontificia Universidad Católica de Chile, Santiago 6513677, Chile;      
^20^Laboratorio de Ecosistemas Marinos y Acuicultura (LEMA), Departamento de 12 Ecología, CUCBA, Universidad de Guadalajara. México. Carr. Guadalajara-Nogales 13 km. 15.5, Las Agujas Nextipac, Zapopan, C.P. 45110, Jalisco, 14, Mexico;     
^21^MARBEC, Université de Montpellier, CNRS, IFREMER, IRD, Montpellier, France     
^*^Correspondance to NMDS (nina.schiettekatte@gmail.com).

**One Sentence Summary:** A global assessment of multiple ecosystem functions reveals critical trade-offs among functions in coral reefs.

**Abstract:** 
Preserving the integrity of coral reefs – their functioning – is a critical challenge of the 21st century. 
However, a quantitative assessment of multiple functions is needed to guide conservation efforts. 
Through the integration of empirically-parametrized bioenergetic models and global community surveys, we quantify five key functions mediated by fishes. 
We show that functions exhibit critical trade-offs driven by diverging community structures. 
Further, functions are locally dominated by few species, but worldwide, the identity of dominant species varies a lot - 70% of the 1110 species in our dataset are locally dominant. 
Our quantitative assessment reveals a challenge in global coral reef conservation: no reef fish community can simultaneously sustain high values across all functions and there are no global keystone species to target.

**Main Text:** 
The flow of elements through biological communities fuels all life on Earth [@Welti2017]. Preserving these fluxes, often termed ecosystem functions, is critical for the integrity of ecosystems [@Welti2017].
For millennia, resources have been managed with an economic mindset to maximize desirable functions such as the production of plant or animal biomass [@Weisser2017].
Sustaining multiple functions likely requires both high species richness and a variety of species assemblages across a landscape [@Zavaleta2010].
However, in agro-ecological settings, efforts to maximize one function negatively impact another (e.g. timber production vs. erosion control), shedding light on the existence of trade-offs between functions [@Tallis2008; @Zavaleta2010].
An understanding of such trade-offs is required to make informed management decisions [@Rodriguez2006], but simultaneously quantifying multiple ecosystem functions is challenging.
Therefore, trade-offs between functions, their drivers, and functional vulnerability are poorly understood in many ecosystems [@Brandl2019front].
